Cataclysmic variables are a key population of gravitational wave sources for LISA

### 2023-06-16 referee_response.txt

We appreciate the referee's careful study of our paper and respond to the comments and questions below inline. Changes to the manuscript are highlighted in bold and referenced by paragraph in the referee response. We hope the referee finds this newly submitted manuscript adeguate.

@@

Beginning p2: rho_CV is not defined.
--> We have now clarified that rho_CV and rho_AMCvn are space densities.

3rd paragraph on p2, about the reason for the period gap: This paragraph is hard to follow, with a lot of jargon (the mass-radius index, an adiabatic value, a stellar vs non-stellar object…).  I would rephrase and/or add more context.
--> We have added a definition of the mass-radius index, clarified that adiabatic mass loss is faster than the radius can respond, and clarified sub-stellar.

Section 2:
Second paragraph:
-I believe something is missing in the first sentence.
--> We have reworded the first sentence.
-How was equation 1 obtained?
--> This equation was obtained empirically such that the period gap limits are enforced during our sampling procedure.

Section 3:
Second to last paragraph: I’m not sure if the considered LDC population does or does not contain interacting binaries given the sentence “For this study, we use the same Galactic population as was used for the LDC2a-v1 data set provided by the LISA Data Chal- lenges (LDCs) (Le Jeune & Babak 2022) which consisted of only de-tached double WD binaries”  and then just after « one which contains detached and accreting double WD binaries from the LDC “.  This seems to be a contradiction.
--> We appreciate the referee pointing out the inconsistency. We have ammended the text to clarify that both detached and interacting double WD binaries are included.

Section 4:
-       ASD is undefined, I think.
            --> ASD is defined just after equation 6 on page 3.
-       Fig2: It would be useful to have the period on the top axis.
            --> We have added the orbital period on the top axis.
-       Fig2: I guess this figure does not include DWD confusion noise?
            --> This is correct; we have clarified this in the caption.
-       End of 2nd paragraph on p4: it’s-> its
            --> We appreciate the catch from the referee and have fixed the typo. 
-       Same sentence: I am not sure I follow the argument here: are you expecting most of the science to be coming from the foreground because the absence of frequency derivative implies lack of chirp mass/distance measurement, which limits the identification of the objects?
    --> This is exactly the reasoning; we have added a clarifying sentence.

-       Second paragraph on p5: I am not sure I understand the implication here: The sources will stop interacting, but they are still emitting GWs. Does this mean that effectively there will be a continuum and without EM counterpart we cannot make any distinction? The measurable feature will only be a pile-up around 80 min? I agree that interacting and non-interaction populations have slightly different evolutions, but given the small population, can we expect this effect to be measurable?
    --> This is a very interesting point. We currently do not know how CVs would evolve through the period gap, but we do think it will not be a smooth continuum in the orbital period distribution of CVs from above to below the gap. In fact structures in the gap population orbital distribution may reveal constraints on the AML mechanism within the gap, which may well be a combitantion of magnetic breaking and GW radiation. Although the latter mechanism is well established, magnetic breaking is very uncertain, and we do not feel a good prediction can be made. In any case, looking at Fig. 2 it will be difficult for LISa to detect a substantial population in the period gap.

### 2023-06-16 src/tex/ms.tex
updated final referee comments

%\kb{commented out what I think is a rogue \pjg}
In order to determine how much the $1~\rm{kpc}$ CV population contributes to the Galactic GW foreground for \lisa\, we must include the effects of the Galactic detached double WD population as well as the \lisa\ constellation orbit. We do this using \texttt{ldasoft} \citep{ldasoft}. For this study, we use the same Galactic population as was used for the LDC2a-v1 data set provided by the \lisa\ Data Challenges (LDCs)~\citep{le_jeune_maude_2022_7132178} which consisted of only detached double WD binaries.  We consider two population cases, one which contains detached and accreting double WD binaries from the LDC and one which adds our $1~\rm{kpc}$ mock population of CVs before modeling the \lisa\ response to the combined signal of each Galactic binary after four years of operations. Together, these two simulations allow us to capture the effects of considering the $1~\rm{kpc}$ CV population in the Galactic foreground.

>>>>

%\kb{commented out what I think is a rogue \pjg}
In order to determine how much the $1~\rm{kpc}$ CV population contributes to the Galactic GW foreground for \lisa\, we must include the effects of the Galactic double WD population as well as the \lisa\ constellation orbit. We do this using \texttt{ldasoft} \citep{ldasoft}. For this study, we use the same Galactic population as was used for the LDC2a-v1 data set provided by the \lisa\ Data Challenges (LDCs)~\citep{le_jeune_maude_2022_7132178} which \textbf{consists of both detached and interacting} double WD binaries.  We consider two population cases, one which contains \textbf{only the double WD binaries from the LDC} and one which adds our $1~\rm{kpc}$ mock population of CVs before modeling the \lisa\ response to the combined signal of each Galactic binary after four years of operations. Together, these two simulations allow us to capture the effects of considering the $1~\rm{kpc}$ CV population in the Galactic foreground.
